\mytitle

### 2023-06-05 chapters/depsynth/abstract.tex
Deambiguate section labels
Change 'this paper' to 'this chapter/work'

This paper presents a new \emph{synthesis-aided} programming model
for building crash-consistent storage systems.
In this approach, storage systems can assume
an \emph{angelic crash-consistency} model,
where the underlying storage stack
promises to resolve crashes in favor of consistency whenever possible.
To realize this model,
we introduce a new \emph{labeled writes} interface for developers to identify their writes to disk,
and develop a program synthesis tool, \depsynth,
that generates \emph{dependency rules}
to enforce crash consistency over these labeled writes.
We evaluate our model in a case study
on a production storage system at a major cloud provider.
We find that \depsynth can automate crash consistency for this complex storage system,
with similar results to existing expert-written code,
and can automatically identify and correct consistency and performance issues.

>>>>

This chapter presents a new \emph{synthesis-aided} programming model
for building crash-consistent storage systems.
In this approach, storage systems can assume
an \emph{angelic crash-consistency} model,
where the underlying storage stack
promises to resolve crashes in favor of consistency whenever possible.
To realize this model,
we introduce a new \emph{labeled writes} interface for developers to identify their writes to disk,
and develop a program synthesis tool, \depsynth,
that generates \emph{dependency rules}
to enforce crash consistency over these labeled writes.
We evaluate our model in a case study
on a production storage system at Amazon Web Services.
We find that \depsynth can automate crash consistency for this complex storage system,
with similar results to existing expert-written code,
and can automatically identify and correct consistency and performance issues.

### 2023-06-05 chapters/depsynth/impl.tex
Change 'this paper' to 'this chapter/work'

Existing work defines a DPLL(T)-style solver for $\tord$ \cite{n:tord},
which we use for solving the constraints specified above and
determining a total order over writes for single litmus tests.
However, by doing so, we empirically found that the solver
slightly diminished the performance of \depsynth for all three of our evaluated case studies
(in the case of \shardstore, slowing the rules search from
\shardstoresynthesistime to \shardstoresynthesistimetord).
Intuitively, we believe this performance degredation is an artifact of 
bad initial assignments from the SAT solver
and a resulting a large number of iterations in the DPLL(T) loop.
For storage systems with increasingly complex behavior,
\depsynth may require much larger litmus tests,
which may make the benefits of searching for orders with $\tord$ more apparent.
However, for the case studies considered in this paper,
we found our original search algorithm from \cref{sec:alg:onetest}
to outperform the $\tord$-directed search.

>>>>

Existing work defines a DPLL(T)-style solver for $\tord$ \cite{n:tord},
which we use for solving the constraints specified above and
determining a total order over writes for single litmus tests.
However, by doing so, we empirically found that the solver
slightly diminished the performance of \depsynth for all three of our evaluated case studies
(in the case of \shardstore, slowing the rules search from
\shardstoresynthesistime to \shardstoresynthesistimetord).
Intuitively, we believe this performance degredation is an artifact of 
bad initial assignments from the SAT solver
and a resulting a large number of iterations in the DPLL(T) loop.
For storage systems with increasingly complex behavior,
\depsynth may require much larger litmus tests,
which may make the benefits of searching for orders with $\tord$ more apparent.
However, for the case studies considered in this chapter,
we found our original search algorithm from \cref{sec:alg:onetest}
to outperform the $\tord$-directed search.

### 2023-06-05 chapters/depsynth/intro.tex
Change 'this paper' to 'this chapter/work'

% this paper: a new programming model for building storage systems in which a program synthesizer automatically
% infers the necessary ordering(?) to guarantee crash consistency.
% two parts:
% 1. instead of programming directly against a low-level disk API, programmers instead build against
%    a higher-level *ordering-aware buffer cache* API. requires programmer to label their writes to disk
%    and then configure the cache with a set of *dependency rules* to realize consistency
% 2. writing those rules is hard, so we develop a synthesizer than can automatically infer the rules
%    necessary to guarantee a desired consistency property. synthesized from a set of examples/litmus
%    tests. great because we can adapt to changes in functionality and in hardware.

@@

This paper presents a new synthesis-aided programming model for building crash-consistent storage systems.
% that \emph{automatically infers} the necessary write-level orderings to guarantee a desired crash consistency property.
The programming model consists of three parts: 
%
a high-level storage interface based on \emph{labeled writes};
%
a synthesis engine for turning labeled writes and a desired crash consistency property 
into a set of \emph{dependency rules} that writes to disk must respect; and 
%
a \emph{dependency-aware buffer cache} that enforces the synthesized rules at run time.
%
Together, these three components let developers keep their implementation free of 
hardcoded optimizations and mechanisms for enforcing consistency. 
%
Instead, developers can focus on the key aspects of their storage system---functional 
correctness, crash consistency, and performance---one at a time. 
%
Their development workflow consists of three steps.

@@

In summary, this paper makes three contributions:
\begin{itemize}
\item A new programming model for building storage systems that automates the implementation of crash consistency guarantees;
\item \depsynth, a synthesis tool that can infer the dependency rules sufficient for a storage system to be crash consistent; and
\item An evaluation showing that \depsynth supports different storage system designs and scales to production-quality systems.
\end{itemize}

\noindent
The remainder of this paper is organized as follows.
\cref{depsynth:s:overview} gives a walk-through of building a simple storage system with \depsynth.
\cref{sec:problem} defines the \depsynth programming model, including labeled writes and dependency rules.
\cref{sec:alg} describes the \depsynth synthesis algorithm for inferring dependency rules,
and \cref{s:impl} details \depsynth's implementation in Rosette.
\cref{sec:eval} evaluates the effectiveness of \depsynth.
\cref{s:related} discusses related work, and \cref{s:conclusion} concludes.\tighten

@@

This paper presents a tool for automatically implementing crash consistency through soft updates
without requiring the developer to reason about the crash states of their system. We develop
\depsynth, a framework for synthesizing \textit{dependency rules} that generate write dependencies
for any execution of the input system. Using \depsynth, we implement a key-value store based
on a simplified version of \todo{ShardStore}. \depsynth synthesizes dependency rules for this
system that generate dependencies similar to those hand-written by experts.
% It would be nicer if I could say that we synthesized rules for several simpler key-value stores as well

@@

To summarize, this paper makes the following contributions:
\begin{enumerate}
  \item \depsynth, the first tool for synthesizing crash consistency code for storage systems
        in the form of soft updates.
  \item A new formalization of the \textit{dependency rule synthesis problem}. % TODO elaborate
  \item A novel backtracking search that enables \depsynth to solve the dependency rule synthesis problem.
  \item An evaluation that shows \depsynth can efficiently generate a set of rules that generalizes
        to outputs outside the training set and that is comparable to expert-written crash consistency code.
\end{enumerate}

The rest of this paper is organized as follows.
\autoref{depsynth:s:overview} illustrates how developers use \depsynth to construct a basic crash consistent storage system.
\autoref{s:problem} formalizes the dependency rule synthesis problem.
\autoref{s:algorithm} presents the \depsynth algorithm for searching for rules over a set of litmus tests.
\autoref{s:impl} provides implementation details.
\autoref{s:eval} evaluates \depsynth.
\autoref{s:related} discusses related work.
\autoref{s:conclusion} concludes.
\fi

>>>>

% this chapter: a new programming model for building storage systems in which a program synthesizer automatically
% infers the necessary ordering(?) to guarantee crash consistency.
% two parts:
% 1. instead of programming directly against a low-level disk API, programmers instead build against
%    a higher-level *ordering-aware buffer cache* API. requires programmer to label their writes to disk
%    and then configure the cache with a set of *dependency rules* to realize consistency
% 2. writing those rules is hard, so we develop a synthesizer than can automatically infer the rules
%    necessary to guarantee a desired consistency property. synthesized from a set of examples/litmus
%    tests. great because we can adapt to changes in functionality and in hardware.

@@

This chapter presents a new synthesis-aided programming model for building crash-consistent storage systems.
% that \emph{automatically infers} the necessary write-level orderings to guarantee a desired crash consistency property.
The programming model consists of three parts: 
%
a high-level storage interface based on \emph{labeled writes};
%
a synthesis engine for turning labeled writes and a desired crash consistency property 
into a set of \emph{dependency rules} that writes to disk must respect; and 
%
a \emph{dependency-aware buffer cache} that enforces the synthesized rules at run time.
%
Together, these three components let developers keep their implementation free of 
hardcoded optimizations and mechanisms for enforcing consistency. 
%
Instead, developers can focus on the key aspects of their storage system---functional 
correctness, crash consistency, and performance---one at a time. 
%
Their development workflow consists of three steps.

@@

In summary, this work makes three contributions:
\begin{itemize}
\item A new programming model for building storage systems that automates the implementation of crash consistency guarantees;
\item \depsynth, a synthesis tool that can infer the dependency rules sufficient for a storage system to be crash consistent; and
\item An evaluation showing that \depsynth supports different storage system designs and scales to production-quality systems.
\end{itemize}

\noindent
The remainder of this chapter is organized as follows.
\cref{depsynth:s:overview} gives a walk-through of building a simple storage system with \depsynth.
\cref{sec:problem} defines the \depsynth programming model, including labeled writes and dependency rules.
\cref{sec:alg} describes the \depsynth synthesis algorithm for inferring dependency rules,
and \cref{s:impl} details \depsynth's implementation in Rosette.
\cref{sec:eval} evaluates the effectiveness of \depsynth.
\cref{s:related} discusses related work, and \cref{s:conclusion} concludes.\tighten

@@

This chapter presents a tool for automatically implementing crash consistency through soft updates
without requiring the developer to reason about the crash states of their system. We develop
\depsynth, a framework for synthesizing \textit{dependency rules} that generate write dependencies
for any execution of the input system. Using \depsynth, we implement a key-value store based
on a simplified version of \todo{ShardStore}. \depsynth synthesizes dependency rules for this
system that generate dependencies similar to those hand-written by experts.
% It would be nicer if I could say that we synthesized rules for several simpler key-value stores as well

@@

To summarize, this work makes the following contributions:
\begin{enumerate}
  \item \depsynth, the first tool for synthesizing crash consistency code for storage systems
        in the form of soft updates.
  \item A new formalization of the \textit{dependency rule synthesis problem}. % TODO elaborate
  \item A novel backtracking search that enables \depsynth to solve the dependency rule synthesis problem.
  \item An evaluation that shows \depsynth can efficiently generate a set of rules that generalizes
        to outputs outside the training set and that is comparable to expert-written crash consistency code.
\end{enumerate}

The rest of this chapter is organized as follows.
\autoref{depsynth:s:overview} illustrates how developers use \depsynth to construct a basic crash consistent storage system.
\autoref{s:problem} formalizes the dependency rule synthesis problem.
\autoref{s:algorithm} presents the \depsynth algorithm for searching for rules over a set of litmus tests.
\autoref{s:impl} provides implementation details.
\autoref{s:eval} evaluates \depsynth.
\autoref{s:related} discusses related work.
\autoref{s:conclusion} concludes.
\fi

### 2023-06-05 chapters/depsynth/problem.tex
Change 'this paper' to 'this chapter/work'

The implementation details of the dependency-aware buffer cache
are outside the scope of this paper and follow the examples of Featherstitch and ShardStore.
An implementation could use a variety of consistency and durability primitives provided by disks,
including force-unit-access writes, cache flush commands, or ordering barriers.
We trust the correctness of the dependency-aware buffer cache,
and specifically we assume it enforces dependency safety (\cref{def:dependency-safety}).

@@

\paragraph{Storage system implementations.}
Developers implement a storage system for \depsynth
by defining a collection of API operations \sys and an implementation function for each operation:
%
\begin{definition}[Storage system implementation]\label{def:storage-system}
A \emph{storage system implementation} $\sys = \{O_a, O_b, \dots\}$
is a set of API operations $O_i$ and,
for each $O_i$,
an \emph{implementation function} $I_{O_i}(d, \vec{x})$
that takes as input a disk state $d$ and a vector of other inputs $\vec{x}$
and issues write operations to mutate disk $d$.
\end{definition}
%
\noindent
\depsynth requires implementation functions to support being symbolically evaluated
with respect to a symbolic disk state $d$.
In this paper, we use Rosette~\cite{torlak:rosette} as our symbolic evaluator;
this allows implementation functions to be written in Racket
and automatically lifted to support the necessary symbolic evaluation,
so long as their executions are deterministic and bounded.

>>>>

The implementation details of the dependency-aware buffer cache
are outside the scope of this chapter and follow the examples of Featherstitch and ShardStore.
An implementation could use a variety of consistency and durability primitives provided by disks,
including force-unit-access writes, cache flush commands, or ordering barriers.
We trust the correctness of the dependency-aware buffer cache,
and specifically we assume it enforces dependency safety (\cref{def:dependency-safety}).

@@

\paragraph{Storage system implementations.}
Developers implement a storage system for \depsynth
by defining a collection of API operations \sys and an implementation function for each operation:
%
\begin{definition}[Storage system implementation]\label{def:storage-system}
A \emph{storage system implementation} $\sys = \{O_a, O_b, \dots\}$
is a set of API operations $O_i$ and,
for each $O_i$,
an \emph{implementation function} $I_{O_i}(d, \vec{x})$
that takes as input a disk state $d$ and a vector of other inputs $\vec{x}$
and issues write operations to mutate disk $d$.
\end{definition}
%
\noindent
\depsynth requires implementation functions to support being symbolically evaluated
with respect to a symbolic disk state $d$.
In this work, we use Rosette~\cite{torlak:rosette} as our symbolic evaluator;
this allows implementation functions to be written in Racket
and automatically lifted to support the necessary symbolic evaluation,
so long as their executions are deterministic and bounded.

### 2023-06-05 chapters/depsynth/related.tex
Change 'this paper' to 'this chapter/work'

Featherstitch~ \cite{frost:featherstitch} introduces a framework that generalizes 
multiple techniques for specifying crash consistency into the
"writes-before" dependencies discussed in this paper.
DepSynth builds on this work by removing the burden of describing
dependencies from the developer.

>>>>

Featherstitch~ \cite{frost:featherstitch} introduces a framework that generalizes 
multiple techniques for specifying crash consistency into the
"writes-before" dependencies discussed in this chapter.
DepSynth builds on this work by removing the burden of describing
dependencies from the developer.

### 2023-06-05 chapters/jitsynth/conclusion.tex
Change 'this paper' to 'this chapter/work'

\section{Conclusion}\label{s:conclusion}
This paper presents a new technique for synthesizing JIT compilers for in-kernel
DSLs. The technique creates per-instruction compilers, or compilers that
independently translate single source instructions to sequences of target
instructions. In order to synthesize each per-instruction compiler, we frame the
problem as search using compiler metasketches, which are optimized using both
read and write set information as well as pre-synthesized load operations. We
implement these techniques in \jitsynth and evaluate \jitsynth over three source
and target pairs from the Linux kernel. Our evaluation shows that (1) \jitsynth
can synthesize correct and performant compilers for real in-kernel languages,
and (2) the optimizations discussed in this paper make the synthesis of these
compilers tractable to \jitsynth. As future in-kernel DSLs are created,
\jitsynth can reduce both the programming and proof burden on developers writing
compilers for those DSLs. The \jitsynth source code is publicly available at
\url{https://github.com/uw-unsat/jitsynth}.

>>>>

\section{Conclusion}\label{jitsynth:s:conclusion}
This chapter presents a new technique for synthesizing JIT compilers for in-kernel
DSLs. The technique creates per-instruction compilers, or compilers that
independently translate single source instructions to sequences of target
instructions. In order to synthesize each per-instruction compiler, we frame the
problem as search using compiler metasketches, which are optimized using both
read and write set information as well as pre-synthesized load operations. We
implement these techniques in \jitsynth and evaluate \jitsynth over three source
and target pairs from the Linux kernel. Our evaluation shows that (1) \jitsynth
can synthesize correct and reasonably performant compilers for real in-kernel languages,
and (2) the optimizations discussed in this chapter make the synthesis of these
compilers tractable to \jitsynth. As future in-kernel DSLs are created,
\jitsynth can reduce both the programming and proof burden on developers writing
compilers for those DSLs. The \jitsynth source code is publicly available at
\url{https://github.com/uw-unsat/jitsynth}.

### 2023-06-05 chapters/jitsynth/intro.tex
Deambiguate section labels
Change 'this paper' to 'this chapter/work'

This paper addresses these challenges with \jitsynth, the first tool for
synthesizing verified JIT compilers for in-kernel DSLs. \jitsynth takes as input
interpreters for the source DSL and the target instruction set architecture
(ISA), and it synthesizes a JIT compiler that is guaranteed to transform each
source program into a semantically equivalent target program. Using \jitsynth,
DSL developers write no proofs or compilers.
Instead, they write the semantics of the source and target
languages in the form of interpreters and a mapping from source to target states,
which \jitsynth trusts to be correct. The
synthesized JIT compiler is implemented in C; thus, it can run directly in the
kernel.\tighten

@@

To summarize, this paper makes the following contributions:
\begin{enumerate}
    \item \jitsynth, the first tool for synthesizing verified JIT compilers for
    in-kernel DSLs, given the semantics of the source and target languages as
    interpreters.\tighten
    \item A novel formulation of the JIT synthesis problem as one of
    synthesizing a per-instruction compiler for \emph{abstract register
    machines}.\tighten
    \item A novel \emph{compiler metasketch} that enables \jitsynth to solve the JIT
    synthesis problem with an off-the-shelf synthesis engine.
    \item An evaluation of \jitsynth's effectiveness, showing that it can
    synthesize verified JIT compilers for three widely used in-kernel DSLs.
\end{enumerate}

The rest of this paper is organized as follows.
%
\autoref{s:overview} illustrates \jitsynth on a small example.
%
\autoref{s:problem} formalizes the JIT synthesis problem for in-kernel DSLs.
%
\autoref{s:algorithm} presents the \jitsynth algorithm for generating and
solving compiler metasketches.
%
\autoref{s:impl} provides implementation details.
%
\autoref{s:eval} evaluates \jitsynth.
%
\autoref{s:related} discusses related work.
\autoref{s:conclusion} concludes.\tighten

>>>>

This chapter addresses these challenges with \jitsynth, the first tool for
synthesizing verified JIT compilers for in-kernel DSLs. \jitsynth takes as input
interpreters for the source DSL and the target instruction set architecture
(ISA), and it synthesizes a JIT compiler that is guaranteed to transform each
source program into a semantically equivalent target program. Using \jitsynth,
DSL developers write no proofs or compilers.
Instead, they write the semantics of the source and target
languages in the form of interpreters and a mapping from source to target states,
which \jitsynth trusts to be correct. The
synthesized JIT compiler is implemented in C; thus, it can run directly in the
kernel.\tighten

@@

To summarize, this chapter makes the following contributions:
\begin{enumerate}
    \item \jitsynth, the first tool for synthesizing verified JIT compilers for
    in-kernel DSLs, given the semantics of the source and target languages as
    interpreters.\tighten
    \item A novel formulation of the JIT synthesis problem as one of
    synthesizing a per-instruction compiler for \emph{abstract register
    machines}.\tighten
    \item A novel \emph{compiler metasketch} that enables \jitsynth to solve the JIT
    synthesis problem with an off-the-shelf synthesis engine.
    \item An evaluation of \jitsynth's effectiveness, showing that it can
    synthesize verified JIT compilers for three widely used in-kernel DSLs.
\end{enumerate}

The rest of this chapter is organized as follows.
%
\autoref{jitsynth:s:overview} illustrates \jitsynth on a small example.
%
\autoref{s:problem} formalizes the JIT synthesis problem for in-kernel DSLs.
%
\autoref{s:algorithm} presents the \jitsynth algorithm for generating and
solving compiler metasketches.
%
\autoref{jitsynth:s:impl} provides implementation details.
%
\autoref{s:eval} evaluates \jitsynth.
%
\autoref{jitsynth:s:related} discusses related work.
\autoref{jitsynth:s:conclusion} concludes.\tighten

### 2023-06-05 chapters/jitsynth/problem.tex
Deambiguate section labels
Change 'this paper' to 'this chapter/work'

An \emph{abstract instruction} (\autoref{def:instruction}) defines the name
(\mathid{op}) and type signature ($\mathcal{F}$) of an operation in the
underlying language. For example, the abstract instruction $(\mathid{addi32}, r
\mapsto \Reg, imm32 \mapsto \BV{32})$ specifies the name and signature of the
\texttt{addi32} operation from the eBPF language
(\autoref{fig:lang-instrs}). Each abstract instruction represents the (finite)
set of all \emph{concrete instructions} that instantiate the abstract
instruction's parameters with values of the right type. For example,
$\cc{addi32}\, 0, 5$ is a concrete instantiation of the abstract instruction for
\cc{addi32}. In the rest of this paper, we will write ``instruction'' to mean a
concrete instruction.\tighten

@@

The general version of our synthesis problem, defined above, uses an arbitrary
equivalence relation $\cong$ between the states of the source and target
machines to determine if a source and target program are semantically
equivalent. \jitsynth can, in principle, solve this problem with the naive
metasketch described in \autoref{s:overview}. In practice, however, the naive
metasketch scales poorly, even on small languages such as toy eBPF and RISC-V\@.
So, in this paper, we focus on source and target ARMs that satisfy an additional
assumption on their state equivalence relation: it can be expressed in terms of
injective mappings from source to target states (\autoref{def:state-equiv}).
%When we write $\cong$ from now on, we mean this restricted form of state equivalence. 
This restriction enables \jitsynth to employ optimizations (such as pre-load
sketches described in \autoref{s:algorithm:pld}) that are crucial to scaling
synthesis to real in-kernel languages.\tighten

>>>>

An \emph{abstract instruction} (\autoref{def:instruction}) defines the name
(\mathid{op}) and type signature ($\mathcal{F}$) of an operation in the
underlying language. For example, the abstract instruction $(\mathid{addi32}, r
\mapsto \Reg, imm32 \mapsto \BV{32})$ specifies the name and signature of the
\texttt{addi32} operation from the eBPF language
(\autoref{fig:lang-instrs}). Each abstract instruction represents the (finite)
set of all \emph{concrete instructions} that instantiate the abstract
instruction's parameters with values of the right type. For example,
$\cc{addi32}\, 0, 5$ is a concrete instantiation of the abstract instruction for
\cc{addi32}. In the rest of this chapter, we will write ``instruction'' to mean a
concrete instruction.\tighten

@@

The general version of our synthesis problem, defined above, uses an arbitrary
equivalence relation $\cong$ between the states of the source and target
machines to determine if a source and target program are semantically
equivalent. \jitsynth can, in principle, solve this problem with the naive
metasketch described in \autoref{jitsynth:s:overview}. In practice, however, the naive
metasketch scales poorly, even on small languages such as toy eBPF and RISC-V\@.
So, in this work, we focus on source and target ARMs that satisfy an additional
assumption on their state equivalence relation: it can be expressed in terms of
injective mappings from source to target states (\autoref{def:state-equiv}).
%When we write $\cong$ from now on, we mean this restricted form of state equivalence. 
This restriction enables \jitsynth to employ optimizations (such as pre-load
sketches described in \autoref{s:algorithm:pld}) that are crucial to scaling
synthesis to real in-kernel languages.\tighten
